A lottery model of density-dependent selection

### 2017-10-26 manuscript.tex
latest

Given the 
For MacArthur, in ``crowded populations ... fitness is $K$'' \citep[pp. 149]{macarthur_1967}. The argument  is quite general,

@@

MacArthur's argument is based on very general 
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2),
\end{equation}
where $n_1$ and $n_2$ are the respective densities of the two types, and the growth rates $f_1$ and $f_2$ decrease with both $n_1$ and $n_2$.

>>>>

MacArthur justified the $r$/$K$ scheme as follows. Consider two types subject to density-dependent population regulation described by
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2), \label{eq:macgeneral}
\end{equation}
where $n_1$ and $n_2$ are the respective densities of the two types, and the growth functions $f_1$ and $f_2$ decrease with both $n_1$ and $n_2$. Now suppose that the population starts growing from low density. Then $n_1$ and $n_2$ will increase until at least one type stops growing; it makes no difference which type, so assume $f_1(n_1,n_2)=0$. Then $n_1$ can never increase again,

Then $n_2$ either keeps growing, or $f_2(n_1,n_2)=0$ as well. In either case, $n_2$ is guaranteed to persist,

if the population is allowed to grow according Eq. \eqref{eq:macgeneral}

persistence depends on being able to grow at higher values of $n_1$ and $n_2$ than the other type in some region. Formally, a type will be excluded unless there are some values of $n_1$ and $n_2$

In the simplest case that each type suppresses its own growth and the growth of the other type equally, $f_1=f_1(N)$ and $f_2=f_2(N)$ only depend on total density $n_1+n_2=N$. If

 and any type that can keep growing

For MacArthur, in ``crowded populations ... fitness is $K$'' \citep[pp. 149]{macarthur_1967}. The argument  is quite general,

@@
